That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-21 ms.tex
update aperture

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a reanalysis of the Hubble observations. We find that the transit light curve is well fit with a single orbiting body, and that the addition of a moon does not significantly improve the fit quality. The $3\,\sigma$ upper limit on the moon radius is FIXME. FIXME: why are we different from TK18?  We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
\end{abstract}

@@

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve. The best was FIXME .

@@

The models also had several fixed parameters. For the moon model, we fixed inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.  We also fixed the moon mass and eccentricity to zero.  For both the no-moon and moon models, we fixed the planet's orbital period to 287.378949 days \citep{teachey18b}. We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.  These choices restrict the orbital FIXME

@@

%We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend. A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}. The model is:
%\begin{equation}
%S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
%\end{equation}
%where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  For comparison, we also fit the raw light curve from \cite{teachey18b}.  We determined the best fit model parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps. We discarded the first 20\% of the MCMC chain as burn-in. As a quick test for convergence, we divided the remainder of the chain in half and checked that the results from the first half were consistent with the second half.

@@

\section{Discussion}
We did not find evidence for the exomoon. Why are we different from Teachey and Kipping?

>>>>

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations from an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality. The $3\,\sigma$ upper limit on the moon radius is FIXME. FIXME: why are we different from TK18?  We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
\end{abstract}

@@

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve. The best was $443  < X < 578$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.

@@

The models also fixes several parameters that are poorly constrained by the light curve shape. For the moon model, we fixed inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.  We also fixed the moon mass and eccentricity to zero.  For both the no-moon and moon models, we fixed the planet's orbital period to 287.378949 days \citep{teachey18b}. We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.

@@

%For more direct comparison with \citep{teachey18b}, we also considered a second systematics model that included three terms: (1) a visit-long second order polynomial trend in time, and (2) a constant offset after orbit 14.
%We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend. A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}. The model is:
%\begin{equation}
%S_{2,i} = c_{j} \times (1 + vt_i + v_2t_i^2)
%\end{equation}
%where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  We determined the best fit model parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps. We discarded the first 20\% of the MCMC chain as burn-in. As a quick test for convergence, we divided the remainder of the chain in half and checked that the results from the first half were consistent with the second half.

@@

\section{Comparison with Teachey \& Kipping 2018}
For comparison, we also fit the raw light curve from \cite{teachey18b}.
